%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=DarkBlue, filecolor=magenta, urlcolor=NavyBlue}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\newcommand{\linkicon}[1]{%
  \href{#1}{\raisebox{-0.15\height}{\faLink}}%
}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jayam Verma} \\ \vspace{1pt}
    Software Development Engineer - Full Stack (Mobile \& Backend) \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 7355068106~ \href{mailto:jayamverma@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{jayamverma@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/jayam-verma-855562160/}{\raisebox{-0.2\height}\faLinkedin\ \underline{Linkedin}}  ~
    \href{https://github.com/Jayamvr007}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
    \href{https://jayam-verma-ios-fintech.lovable.app/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology Hamirpur }{Jul. 2017 -- May 2021}
      {B.Tech: Electronics And Communication Engineering}{Hamirpur, H.P.}
  \resumeSubHeadingListEnd

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\item{
Software Development Engineer with \textbf{4.4 years} of experience building \textbf{scalable} mobile and backend systems for \textbf{finance} and \textbf{media} domains. Specialized in \textbf{iOS} (Swift, SwiftUI), \textbf{Backend} (Python, FastAPI), and \textbf{Real-time Systems}. Proven expertise in \textbf{distributed architecture}, \textbf{video streaming}, and \textbf{WebSocket communication}. Passionate about leading end-to-end development, from designing resilient APIs to crafting polished, high-performance user interfaces used by \textbf{millions of users}.
}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
{FIBE (formerly Earlysalary) $|$ \emph{Swift, SwiftUI, Python, FastAPI} {\small (\href{https://apps.apple.com/in/app/fibe-instant-personal-loan-app/id1094602630}{App Store})}}{Jul 2024 -- present}
      {Senior iOS Engineer }{Pune, Maharashtra}
     \resumeItemListStart
     \resumeItem{Built the UI layer for FiBE's \textbf{UPI Payment System}, handling Registration, UPI Lite, and Mandate flows, ensuring a seamless user experience.}
     \resumeItem{Contributed to backend microservices using \textbf{Python} and \textbf{FastAPI}, optimizing API response payloads for mobile clients and improving success rates by \textbf{15\%} for the UPI module.}
     \resumeItem{Transformed the static \textbf{KYC journey} into a \textbf{server-driven dynamic flow}, allowing configurable steps (Selfie, Video KYC, etc.) without app updates.}
     \resumeItem{Revamped the \textbf{Disbursement} module using \textbf{MVVM}, enabling dynamic loan terms and promo codes, which boosted disbursals by \textbf{20\%} for 80K+ users.}
        \resumeItem{Designed a \textbf{Referral System} that drove \textbf{25\%} user acquisition growth, rewarding users with Fibecoins and vouchers.}
        \resumeItem{Developed key engagement features like \textbf{Scratch Cards} and \textbf{Fixed Deposits} (via UpSwing SDK), driving 10,000+ new investment accounts.}
        \resumeItem{Led \textbf{code reviews} and defined iOS coding standards to improve team velocity and code quality.}
      \resumeItemListEnd
\resumeSubheading
{Rakupa Technologies (sub. Whiz Technologies) $|$ \emph{Swift, AVFoundation, Xcode}{\small (\href{https://apps.apple.com/in/app/wtva-9-news/id1188060806}{App Store})}}{June 2023 -- July 2024}
      {iOS Developer}{Pune, Maharashtra}
     \resumeItemListStart
        \resumeItem{Contributed to over \textbf{125+ media apps} (Griffin News, Beasley, etc.) focusing on \textbf{video streaming} and HLS playback.}
        \resumeItem{Optimized \textbf{video discovery} and playback performance using \textbf{AVFoundation}, ensuring smooth streaming across varying network conditions.}
        \resumeItem{Integrated \textbf{Weather SDKs} and implemented detailed event tracking (mParticle) for user analytics.}
        \resumeItem{Deployed \textbf{20+ apps} with targeted push notifications, increasing daily active users by keeping audiences engaged with real-time news alerts.}
      \resumeItemListEnd
\resumeSubheading
{LTIMindtree $|$ \emph{Swift, Xcode} {\small (\href{https://apps.apple.com/gb/app/m-s-banking/id965170355}{App Store})}}
{Jul 2021 -- Apr 2023}
      {Software Engineer}{Pune, Maharashtra}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Apple Pay In-App Provisioning} for \textbf{HSBC Mobile Banking}, streamlining card additions for 100K+ customers.}
        \resumeItem{\textbf{Researched and integrated 15+ REST APIs} to enhance transaction efficiency by \textbf{30\%} through mobile payment platforms.}
        \resumeItem{Collaborated across distributed teams using Git/Jira to optimize workflows and reduce issue resolution times.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-8pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-6pt}
    \resumeSubHeadingListStart
    
    \resumeProjectHeading
    {\textbf{Sentinel - Real-time Stock Intelligence} {\small (\href{https://github.com/Jayamvr007/sentinal}{GitHub})}}
    {January 2026}
    \resumeSubSubheading
    {Full Stack Real-time Finance App $|$ \emph{SwiftUI, Python (FastAPI), WebSockets, Next.js}}{}
    \resumeItemListStart
      \resumeItem{Built a real-time stock tracker using \textbf{FastAPI} and \textbf{WebSockets}, handling \textbf{1,000+ updates/sec} with sub-50ms latency.}
      \resumeItem{Developed an iOS app with \textbf{Live Activities} and \textbf{Dynamic Island}, displaying live prices on the Lock Screen with zero battery drain.}
      \resumeItem{Created a custom alerting engine using \textbf{APNs} and \textbf{SQLAlchemy} to deliver instant notifications for price thresholds.}
      \resumeItem{Designed a synchronized \textbf{Next.js} web dashboard that shares real-time WebSocket streams with the mobile app.}
    \resumeItemListEnd
    \vspace{-13pt}

    \resumeProjectHeading
{\textbf{SETTLE} {\small (\href{https://github.com/Jayamvr007/settle}{GitHub})}}
{December 2025}
\resumeSubSubheading
{Group Expense Splitting \& Debt Management iOS App $|$ \emph{SwiftUI, Firebase, MVVM, Core Data}}{}
\resumeItemListStart
  \resumeItem{Engineered a \textbf{debt simplification algorithm} that reduces settlement transactions by \textbf{70\%}.}
  \resumeItem{Implemented \textbf{dual authentication} (Google + Phone OTP) and UPI payment integration with sub-100ms response times.}
  \resumeItem{Designed \textbf{15+ reusable SwiftUI components} for complex splitting modes and real-time balance updates.}
 \resumeItem{Implemented on-device \textbf{CoreML} suggestions for expense categories with >85\% accuracy.}
\resumeItemListEnd
\vspace{-13pt}
      
      \resumeProjectHeading
{\textbf{Clima} {\small (\href{https://github.com/Jayamvr007/Clima_App}{GitHub})} $|$ \emph{Swift, Xcode}}{January 2021}
          \resumeItemListStart
            \resumeItem{Weather app fetching real-time data for 100+ cities using REST APIs and Core Location.}
            \resumeItem{Used Delegate pattern to reduce code redundancy by 20\% and optimized GPS retrieval accuracy.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-13pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Swift, Python, SQL, TypeScript, React JS, Dart, Objective C, C++, JavaScript, HTML, CSS, Kotlin, DSA} \\
     \textbf{Backend \& Web}{: FastAPI, Next.js, Node.js, SQLAlchemy, Pydantic, WebSockets, RESTful APIs, GraphQL, SQLite, PostgreSQL, Docker} \\
     \textbf{iOS \& Mobile}{: SwiftUI, UIKit, Flutter, AVFoundation, AVPlayer, CoreData, Combine, Swift Concurrency, Live Activities, Dynamic Island, APNs, HLS Streaming, Auto Layout, Core Animation, In-App Purchases} \\
     \textbf{Developer Tools}{: Xcode, Android Studio, VS Code, Git, Jenkins, Fastlane, Bazel, Firebase, Postman, Jira/Confluence, TestFlight} \\
     \textbf{Architecture}{: MVVM, VIPER, Clean Architecture, Distributed Systems, Microservices, Design Patterns} \\
     \textbf{Performance}{: Low-latency Networking, Memory Management, AsyncIO, App Optimization} \\
     \textbf{AI \& LLM Tools}{: LLM, RAG, LangChain, Github Copilot, Claude Sonnet, ChatGPT-4} \\
    }}
 \end{itemize}
 \vspace{-10pt}

 %-----------LANGUAGES-----------
\section{Languages}
\vspace{0pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \small English (Fluent), Hindi (Native)
\end{itemize}
\vspace{-10pt}
        
\end{document}
